Classical probability measures as pullback of quantum probability measures?

### 2022-04-22 pullback.tex
pullback.lyx Commit a successful compiled lyx file for debugging...

%% LyX 2.3.6.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1,T2A]{fontenc}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{rotfloat}
\usepackage{setspace}
\usepackage[all]{xy}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

@@

\maketitle
As discussed in Sec.~\ref{subsec:Classical-and-Quantum}, the quantum
probability spaces could be thought as a big space glued by ``local''
classical probability space defined by each orthonormal basis~$\Omega$
according to the map $\varphi:2^{\Omega}\rightarrow\events$ defined
in Eq.~(\ref{eq:pullback-function}) which sends a classical event
$E\in2^{\Omega}$ to a quantum event $\varphi\left(E\right)\in\events$.
Then, for any quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$,
the function $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)\colon2^{\Omega}\rightarrow\left[0,1\right]$
defined by precomposition is a classical probability measure\footnote{\begin{proof}
\begin{subequations}\label{eq:CPM-constraints}
 &  & \mu\left(\varphi(\Omega)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
 &  & \mu\left(\varphi\left(\overline{E}\right)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
 &  & \mu\left(\varphi(\emptyset)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-complement})}}{=}1-\mu\left(\varphi\left(\Omega\right)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-necess})}}{=}0\,,\label{eq:CPM-imposs}
and for each pair of disjoint $E_{0}$ and $E_{1}$, we have 
\[
\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}\varphi\left(\emptyset\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mathbb{0}\,,
\]
i.e., $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
are orthogonal, and then: 
\begin{aligned} & \mu\left(\varphi\left(E_{0}\cup E_{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(\emptyset\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:QuantumProbability-Addition})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)\right)+\mu\left(\varphi\left(E_{1}\right)\right)\,.
\end{aligned}
\label{eq:Probability-Addition}
\end{proof}}. Since that ``precomposition'' is called ``pullback'' in differential
geometry~\cite{wiki:Pullback}\footnote{Whether this kind of ``pullback'' is categorical will need further
investigate.}, we will use their notation, write the precomposition $\left(\lambda E.\mu\left(\varphi\left(E\right)\right)\right)$
as $\lambda E.\left(\varphi^{*}\mu\right)\left(E\right)$, i.e., $\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)$,
call $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
the pullback of $\mu$ by $\varphi$, and summarize how ``pullback''
preserves their structures in Table~\ref{tab:Comparison}. 
\begin{sidewaystable}
\noindent \centering{}\caption{\label{tab:Comparison}Comparison between the classical and quantum
measurement processes with real-valued probability for finite dimensional
cases}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{YYYY}
\toprule 
Name & Classical & Quantum & How does the structure preserve?\tabularnewline
\midrule
\midrule 
Event & $E\in2^{\Omega}$ & $\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\in\events$ & Eqs.~(\ref{eq:pullback-properties-basic}) and~(\ref{eq:pullback-properties})\tabularnewline
\midrule 
Probability measure & $\begin{array}{cccc}
\varphi^{*}\mu\colon & 2^{\Omega} & \rightarrow & \left[0,1\right]\\
 & E & \mapsto & \mu\left(\varphi\left(E\right)\right)
\end{array}$ & $\begin{array}{cccc}
\mu\colon & \events & \rightarrow & \left[0,1\right]\\
 & P & \mapsto & \mu\left(P\right)
\end{array}$ & Eqs.~(\ref{eq:CPM-constraints}) and~(\ref{eq:Probability-Addition})\tabularnewline
\midrule
\midrule 
Possible measured values & $\lambda_{i}\in\mathbb{R}$ & $\lambda_{i}\in\mathbb{R}$ & Equal\tabularnewline
\midrule 
The event to measure $\lambda_{i}$ & $E_{i}\in2^{\Omega}$ & $\varphi\left(E_{i}\right)\in\events$ & Mapped by $\varphi$\tabularnewline
\midrule 
The probability that the measured value is $\lambda_{i}$ & $\left(\varphi^{*}\mu\right)\left(E_{i}\right)=\mu\left(\varphi\left(E_{i}\right)\right)\in\left[0,1\right]$ & $\mu\left(\varphi\left(E_{i}\right)\right)\in\left[0,1\right]$ & Equal\tabularnewline
\midrule 
Summarize the measurement process as & random variable $\varphi^{*}\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{E_{i}}$ & observable $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}\varphi\left(E_{i}\right)$ & \tabularnewline
\midrule 
Expectation value & $\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(E_{i}\right)$ & $\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(E_{i}\right)\right)$ & Equal, and proved in Lemma~\ref{lemma:real-expectation-value-between-classical-quantum}\tabularnewline
\midrule
\midrule 
Probability measure could be simplified as & probability mass function $m:\Omega\rightarrow[0,1]$ such that $\left(\varphi^{*}\mu\right)\left(E\right)=\sum_{\omega\in E}m\left(\omega\right)$ & mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$ such that $\mu\left(P\right)=\Tr\left(\rho P\right)$ & \tabularnewline
\midrule 
 & Need a notation for $\varphi^{*}\mu\mapsto m$ to keep going & Need a notation for $\mu\mapsto\rho$ to keep going & We may draw commuting diagram here?\tabularnewline
\midrule 
The probability that the measured value is $\lambda_{i}$ &  &  & \tabularnewline
\midrule 
Expectation value &  &  & \tabularnewline
\midrule
\midrule 
Post-measurement state &  &  & \tabularnewline
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{sidewaystable}
We can then extend this table to compare between the classical and
quantum measurement processes to get real numbers. It is clear that
each step of the measurement process is exactly equal or just mapped
by $\varphi$ except we summarize classical measurement process as
random variable, but summarize quantum measurement process as observable.
Notice that after we fix an orthonormal basis~$\Omega$, $\varphi$
is actually an invertible map so that given an observable $\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$,
we can define an unique random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
corresponding to $\mathbf{O}$. Therefore, we call this random variable
as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
has a push forward observable. This is better in a sense that we don't
have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
for different orthonormal bases, but every theorem for IVPMs starts
from the quantum part with an observable, so we need the notation
$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
the formula computing expectation values and the the post-measurement-state
postulates after we define a notation to send probability measures
to states and the other way around.

@@

\subsection{Classical and Quantum Probability Spaces\label{subsec:Classical-and-Quantum}}

@@

Since the previous abstraction doesn't specify the process to generate
the outcomes, this process could well be a quantum experiment. Let
us prepare a beam of one kind of spin~$1$ particles whose state
can be characterized by a vector in three-dimen\-sional Hilbert space
with basis vectors $\ket{0}$, $\ket{1}$, and $\ket{2}$. In principle,
this beam can be split by a Stern-Gerlach type experiment according
to the eigenvalues of the observable $\mathbf{O}_{0}$ with spectral
decomposition 
\begin{equation}
\mathbf{O}_{0}=0\,\proj{0}+1\,\proj{1}+2\,\proj{2}\,,\label{eq:observable}
\end{equation}
and the states corresponding to the split beams are $\ket{0}$, $\ket{1}$,
and $\ket{2}$ \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
Instead of sending a beam of particles, if only one particle is sent
to the beam splitter, the state of the particle after the experiment
is one of $\ket{0}$, $\ket{1}$, and $\ket{2}$, and there is a probability
to get each post-experimental state. In the language of our abstraction,
the set of outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$.
All possible events are $\emptyset$, $\left\{ \ket{0}\right\} $,
$\left\{ \ket{1}\right\} $, $\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
and $\Omega_{0}$. And this experiment defines a classical probability
measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
sending exactly the same particle as the previous one but using a
different beam splitter corresponding to the observable $\mathbf{O}_{1}$
with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
defined by this experiment is different from the previous one, these
two experiments may produce the same post-experimental state~$\ket{2}$,
and the probability of the common event $\left\{ \ket{2}\right\} $
is believed to be the same, i.e., 
\begin{equation}
\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
\end{equation}
In general, as long as sending the same particle, the probability
of the same event in different experiments should always be the same.
This fact is equivalent to the fact that commuting observables could
be measured simultaneously which is essential to define contextuality
and will be explained in Sec.~\ref{sec:Kochen-Specker}.

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but represent
the same situation. For example, if we take the complement on both
sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
these events should be identified as the same quantum event to simplify
our discussion. This identification can be achieved by mapping a classical
event~$E$ to the projector generated by $E$,
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
\begin{equation}
\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
\end{equation}
In general, if two classical events~$E$ and $E'$ are mapped to
the same projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
then the probability of $E$ is the same as the probability of $E'$.
Therefore, for any classical event~$E$, its corresponding quantum
event is defined to be the projector $\varphi\left(E\right)$, and
the set of all projectors on a given Hilbert space is called a quantum
event space~$\events$.

This function $\varphi$ not only respects the probability of events
but also naturally sends the set structure to the corresponding projector
structure:
\begin{align}
\varphi\left(\Omega\right) & =\mathbb{1}\,, & \varphi\left(\overline{E}\right) & =\mathbb{1}-\varphi\left(E\right)\,.\label{eq:pullback-properties-basic}
\end{align}
Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
exists a pair of events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$
such that $P_{0}=\varphi\left(E_{0}\right)$ and $P_{1}=\varphi\left(E_{1}\right)$.
Conversely, given a pair of events $E_{0}$ and $E_{1}$ in the same
sample space~$\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are commuting and satisfying the
following properties: 
\begin{align}
\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
\end{align}
Moreover, $E_{0}$ and $E_{1}$ are disjoint if and only if $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.

Then, a quantum probability space can be defined as a quantum event
space~$\events$ together with a quantum probability measure $\mu\colon\events\rightarrow\left[0,1\right]$
subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of orthogonal projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Because $\varphi$ respects the probability of events, if we restrict
the domain of $\varphi$ on a classical event space $2^{\Omega}$,
the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
defined by precomposition 
\begin{equation}
\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)\label{eq:classical-pullback}
\end{equation}
is a classical probability measure and called the pullback of $\mu$
by $\varphi\colon2^{\Omega}\rightarrow\events$.

Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
assignment for every projector $P$, we can define the expectation
value of an observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
as \cite{544199,Jaeger2007}: 
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
\end{equation}
where the subscript $\mu$ might be omitted if it is clear according
to the context. This definition is also consistent with the classical
expectation values because we can pullback an observable to a classical
random variable, and the expectation values are invariant.

>>>>

%% LyX 2.3.6.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1,T2A]{fontenc}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{rotfloat}
\usepackage{setspace}
\usepackage[all]{xy}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

@@

\maketitle
It is clear that each step of the measurement process is exactly equal
or just mapped by $\varphi$ except we summarize classical measurement
process as random variable, but summarize quantum measurement process
as observable. Notice that after we fix an orthonormal basis~$\Omega$,
$\varphi$ is actually an invertible map so that given an observable
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, we can define an unique
random variable $\sum_{i=0}^{D-1}\lambda_{i}\mathbf{1}_{\varphi^{-1}\left(P_{i}\right)}$
corresponding to $\mathbf{O}$. Therefore, we call this random variable
as the pullback of $\mathbf{O}$ by $\varphi$, and denoted by $\varphi^{*}\mathbf{O}$.\footnote{We might also choose the other way around so that each random variable
has a push forward observable. This is better in a sense that we don't
have the ambiguity that $\varphi^{*}\mathbf{O}$ is might be different
for different orthonormal bases, but every theorem for IVPMs starts
from the quantum part with an observable, so we need the notation
$\varphi^{*}\mathbf{O}$ and fixing an orthonormal basis to disambiguate
$\varphi^{*}\mathbf{O}$ anyway.} According to Gleason's theorem, the table could be extended to simplify
the formula computing expectation values and the the post-measurement-state
postulates after we define a notation to send probability measures
to states and the other way around.

@@

\subsection{Classical Probability Space\label{subsec:Classical-and-Quantum}}

@@

Since the previous abstraction doesn't specify the process to generate
the outcomes, this process could well be a quantum experiment. Let
us prepare a beam of one kind of spin~$1$ particles, and split it
by an inhomogeneous magnetic field along the $z$-axis as a well-known
Stern-Gerlach type experiment \cite{:/content/aip/journal/jmp/21/1/10.1063/1.524312,peres1995quantum}.
This beam will be split into three beams, and we will call the outcome
beams bent up as $\ket{0}$, bent down as $\ket{1}$, and not-bent
as $\ket{2}$. Instead of sending a beam of particles, if only one
particle is sent to the beam splitter, we will only get one of the
outcomes $\ket{0}$, $\ket{1}$, and $\ket{2}$, and there is a probability
to get each outcome. In the language of our abstraction, the set of
outcomes is $\Omega_{0}=\{\ket{0},\ket{1},\ket{2}\}$. All possible
events are $\emptyset$, $\left\{ \ket{0}\right\} $, $\left\{ \ket{1}\right\} $,
$\left\{ \ket{2}\right\} $, $\left\{ \ket{0},\ket{1}\right\} $,
$\left\{ \ket{0},\ket{2}\right\} $, $\left\{ \ket{1},\ket{2}\right\} $,
and $\Omega_{0}$. Each time we perform this experiment, it induces
a classical probability measure $\mu_{0}\colon2^{\Omega_{0}}\rightarrow\left[0,1\right]$.
Moreover, if we prepare the particles in the ``same'' way as the
particle inducing $\mu_{0}$, they will induce the same classical
probability measure $\mu_{0}$.

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
sending the ``same'' particle as the previous one, but we rotate
the inhomogeneous magnetic field $90\lyxmathsym{\textdegree}$ and
now along the $x$-axis. This time we call the outcome beams bent
left as $\ket{\ps}$, bent right as $\ket{\ms}$, and not-bent still
as $\ket{2}$. Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
defined by this experiment is different from the previous one, they
all produce a not-bent outcome~$\ket{2}$, and the probability of
the common event $\left\{ \ket{2}\right\} $ is believed to be the
same, i.e., 
\begin{equation}
\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
\end{equation}

Since we may rotate the inhomogeneous magnetic field any degree~$\theta$,
it is nature to represent the two bent outcomes as $\sin\theta\ket{0}+\cos\theta\ket{1}$
and $\cos\theta\ket{0}-\sin\theta\ket{1}$. Then, $\ket{\ps}$ and
$\ket{\ms}$ can be represented as $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$. Conventionally
\cite{peres1995quantum}, we will then postulate any normalized complex
vector spanned by $\ket{0}$, $\ket{1}$, and $\ket{2}$ could be
a measurement outcome, any orthonormal basis form a sample space,
and sending a particle to this orthonormal basis inducing a classical
probability measure. In general, as long as sending the same particle,
the probability of the same event in different experiments should
always be the same, i.e., giving two induced classical probability
measures $\mu'\colon2^{\Omega'}\rightarrow\left[0,1\right]$ and $\mu''\colon2^{\Omega''}\rightarrow\left[0,1\right]$,
the probabilities of getting $E\subseteq\Omega'\cap\Omega''$ are
the same
\begin{equation}
\mu'\left(E\right)=\mu''\left(E\right)\,.\label{eq:mu-equal-same-event}
\end{equation}
\footnote{This fact is equivalent to the fact that commuting observables could
be measured simultaneously which is essential to define contextuality
and will be explained in Sec.~\ref{sec:Kochen-Specker}... Or maybe
there is a gap between outcomes in a few types of experiments and
every normalized vector in a Hilbert space could be an outcome, but
inducing latter from axioms seems a bit too much here\ldots}

\subsection{Quantum Probability Space}

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but represent
the same situation. For example, if we take the complement on both
sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
these events should be identified as the same quantum event to simplify
our discussion. This identification can be achieved by mapping a classical
event~$E$ to the projector generated by $E$,\footnote{Should we prove whether there is no other way to identify?}
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
\begin{equation}
\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
\end{equation}

In general, this function $\varphi$ naturally sends the set structure
to the corresponding projector structure:
\begin{align}
\varphi\left(\Omega\right) & =\mathbb{1}\,, & \varphi\left(\overline{E}\right) & =\mathbb{1}-\varphi\left(E\right)\,.\label{eq:pullback-properties-basic}
\end{align}
Given two \emph{commuting} projectors $P_{0}$ and~$P_{1}$, there
exists a pair of events $E_{0}$ and $E_{1}$ in the same sample space~$\Omega$
such that $P_{0}=\varphi\left(E_{0}\right)$ and $P_{1}=\varphi\left(E_{1}\right)$.
Conversely, given a pair of events $E_{0}$ and $E_{1}$ in the same
sample space~$\Omega$, their corresponding quantum events $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are commuting and satisfying the
following properties: 
\begin{align}
\varphi\left(E_{0}\cap E_{1}\right) & =\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,, & \varphi\left(E_{0}\cup E_{1}\right) & =\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\,.\label{eq:pullback-properties}
\end{align}
Moreover, $E_{0}$ and $E_{1}$ are disjoint if and only if $\varphi\left(E_{0}\right)$
and $\varphi\left(E_{1}\right)$ are orthogonal, where two projectors
$P_{0}$ and $P_{1}$ are called \emph{orthogonal} if $P_{0}P_{1}=\mathbb{0}$.
Because the structure is preserved by $\varphi$, so does the probability
of events.

\begin{lemma}Consider two classical events $E'\subseteq\Omega'$
and $E''\subseteq\Omega''$ are mapped to the same projector, i.e.,
$\varphi\left(E'\right)=\varphi\left(E''\right)$. Even if their experimental
outcomes $\Omega'$ and $\Omega''$ may be different, when sending
the ``same'' particle to these two experiments, and inducing two
classical probability measures $\mu'\colon2^{\Omega'}\rightarrow\left[0,1\right]$
and $\mu''\colon2^{\Omega''}\rightarrow\left[0,1\right]$, the probability
of getting $E'$ is the same as the probability of getting $E''$,
i.e., $\mu'\left(E'\right)=\mu''\left(E''\right)$.\end{lemma}

\begin{proof}Consider the outcomes in the complement event of $E''$,
$\Omega''\backslash E''$. Because $\varphi\left(E'\right)=\varphi\left(E''\right)$,
every outcomes in $\Omega''\backslash E''$ is orthogonal to $E'$,
and $\Omega'''=E'\cup\left(\Omega''\backslash E''\right)$ is an orthonormal
basis. Consider its inducing classical probability measure $\mu'''\colon2^{\Omega'''}\rightarrow\left[0,1\right]$,
we have
\[
\mu'\left(E'\right)\overset{\textrm{Eq.~(\ref{eq:mu-equal-same-event})}}{=}\mu'''\left(E'\right)=1-\mu'''\left(\Omega''\backslash E''\right)\overset{\textrm{Eq.~(\ref{eq:mu-equal-same-event})}}{=}1-\mu''\left(\Omega''\backslash E''\right)=\mu''\left(E''\right)\,.
\]
\end{proof}

Therefore, for any classical event~$E$, its corresponding quantum
event is defined to be the projector $\varphi\left(E\right)$, and
the set of all projectors on a given Hilbert space is called a quantum
event space~$\events$. Then, a quantum probability space can be
defined as a quantum event space~$\events$ together with a quantum
probability measure $\mu\colon\events\rightarrow\left[0,1\right]$
subject to the corresponding constraints \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012}:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of orthogonal projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Because $\varphi$ respects the structure of events, it also respects
probability measures according to precomposition.

\begin{lemma}If we restrict the domain of $\varphi$ on a classical
event space $2^{\Omega}$, the function $\varphi^{*}\mu\colon2^{\Omega}\rightarrow\left[0,1\right]$
defined by precomposition 
\begin{equation}
\left(\varphi^{*}\mu\right)\left(E\right)=\mu\left(\varphi\left(E\right)\right)\label{eq:classical-pullback}
\end{equation}
is a classical probability measure.\end{lemma}

\begin{proof}
\begin{subequations}\label{eq:CPM-constraints}
\begin{eqnarray}
 &  & \mu\left(\varphi(\Omega)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1\,,\label{eq:CPM-necess}\\
 &  & \mu\left(\varphi\left(\overline{E}\right)\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mu\left(\mathbb{1}-\varphi\left(E\right)\right)\overset{\textrm{Eq.~(\ref{eq:QuantumProbability})}}{=}1-\mu\left(\varphi\left(E\right)\right)\,,\label{eq:CPM-complement}\\
 &  & \mu\left(\varphi(\emptyset)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-complement})}}{=}1-\mu\left(\varphi\left(\Omega\right)\right)\overset{\textrm{Eq.~(\ref{eq:CPM-necess})}}{=}0\,,\label{eq:CPM-imposs}
\end{eqnarray}
\end{subequations}
and for each pair of disjoint $E_{0}$ and $E_{1}$, we have 
\[
\varphi\left(E_{0}\right)\varphi\left(E_{1}\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}\varphi\left(\emptyset\right)\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}\mathbb{0}\,,
\]
i.e., $\varphi\left(E_{0}\right)$ and $\varphi\left(E_{1}\right)$
are orthogonal, and then: 
\begin{equation}
\begin{aligned} & \mu\left(\varphi\left(E_{0}\cup E_{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)-\varphi\left(\emptyset\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:pullback-properties-basic})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)+\varphi\left(E_{1}\right)\right)\\
\overset{\textrm{Eq.~(\ref{eq:QuantumProbability-Addition})}}{=}{} & \mu\left(\varphi\left(E_{0}\right)\right)+\mu\left(\varphi\left(E_{1}\right)\right)\,.
\end{aligned}
\label{eq:Probability-Addition}
\end{equation}
\end{proof}
